\todo{INGRID: Creating Languages in MPS by Importing ANTLR Grammars}

### 2016-09-23 chapters/background.tex
Notes to evaluation

The key takeaways from the mps-metabnf project are that the intermediate grammar MPS representation, when finished, will offer some powerful means of adjustment.
Using the projectional editor, the user can easily specify information about the code layout, export the target MPS language and in case further adjustments are needed, come back to the grammar definition and fix any problems.
The MPS language of the grammar definition can be easily extended with needed features (indenting, line breaks...), which is superior to our approach.

It also has some downsides.
Because MPS doesn't offer any tools that would allow easy transformation from the MPS grammar to the MPS language, the second step of the import process hasn't been implemented yet and will be probably very problematic.
Another downside might be the need for a double transformation implementation -- first one being the import of the text grammar to the MPS grammar definition.

>>>>

The key takeaways from the mps-metabnf project are that the intermediate grammar MPS representation, when finished, will offer some powerful means of adjustment.
Using the projectional editor, the user can easily specify information about the code layout, export the target MPS language and, in case further adjustments are needed, come back to the grammar definition, fix any problems and regenerate the language.
The MPS language of the grammar definition can be easily extended with needed features (indenting, line breaks...), which is superior to our approach, because they can be represented using many visual means.

This approach also has some downsides.
Because MPS doesn't offer any tools that would allow easy transformation from the MPS grammar to the MPS language, the second step of the import process hasn't been implemented yet and will be probably very problematic.
Another downside might be the need for a double transformation implementation -- first one being the import of the text grammar to the MPS grammar definition.

From another point of view -- for each additional feature, that we decide to add to the grammar notation, we need to implement a corresponding transformation.
This subsequently leads to duplicating the projectional editor that is already present in MPS.
This means that there needs to be a line drawn between which features are added and which will be left for the user to add to the target language using MPS.

### 2016-09-23 chapters/evaluation.tex
Notes to evaluation

In order to evaluate INGRID, we tried to import several real/mainstream languages:
\begin{itemize}
	\item \textbf{SimpleXML} --- Simplified XML that we used in this thesis for explanatory purposes.
	\item \textbf{JSON} --- Similar to XML, but this time a full port of the specification.
	\item \textbf{ECMAScript 5.1} --- Specification of the language known as JavaScript, dated to the year 2011, which is currently the most frequently adopted version.
\end{itemize}
Results of the import process are included in the package that is available at \todo{url}.
The repository \todo{Add url} contains an example MPS project. There are three languages.
For each example language, you can find its original import, exactly in the form as created by our plugin.

We experimented with import of XML, JavaScript, Python, and maybe some other languages.

These general purpose languages are quite complex when it comes to their structure and the overall syntax variety.

We must emphasize that the automatically imported languages are not ready-to-use full-fledged MPS languages.
We did not expect to achieve that at this stage, as that is a much bigger, if not impossible, challenge.
Imported languages contain full structure found in the respective grammars and some more aspect definitions that will help users of the languages in creating code.
The imported language has to be manually adjusted (tweak, polished) by the end user (developer) and some of its complications have to be resolved manually by a human.

@@

Our main goal was to prove that even though our method (plugin) does not create a perfect language, it can be customized very fast into a very usable form.
We manually tweaked/customized the editor and the TextGen aspect only, structure aspect was left in its original form.
This justifies some of the decisions we have described in Section X (editor aspect) and Section Y (textgen), proving that our approach is quite practical (and the best).

@@

To summarize, import languages such as JavaScript, JSON, MySQL and others is giving nice results.

@@

Limitation: the project is lacking proper error reporting and cannot handle cyclic rules (which could be found in Python grammar, for example).

>>>>

In order to evaluate INGRID, we tried to import several real/mainstream languages:
\begin{itemize}
	\item \textbf{SimpleXML} --- Simplified XML that we used in this thesis for explanatory purposes.
	\item \textbf{JSON} --- Similar to XML, but this time a full port of the specification.
	\item \textbf{ECMAScript 5.1} --- Specification of the language known as JavaScript, dated to the year 2011, which is currently the most frequently adopted version.
\end{itemize}
Results of the import process are included in the package that is available at \todo{url}.
The repository \todo{Add url} contains an example MPS project with three languages.
For each example language, you can find its original import, exactly in the form as created by our plugin.

We experimented with import of XML, JavaScript, Python, Ruby, C#, Swift, MySQL and some other languages.

Most of these languages are quite complex when it comes to their structure and the overall syntax variety.

We must emphasize that the automatically imported languages are not ready-to-use full-fledged MPS languages.
We did not expect to achieve that at this stage, as that is a much bigger, if not impossible, challenge.
Imported languages contain full structure found in the respective grammars and some more aspect definitions that will help users of the languages in creating code.
\PV{The imported language has to be manually tweaked by the end user.}
The imported language has to be manually adjusted (tweak, polished) by the end user (developer) and some of its complications have to be resolved manually by a human.

@@

Our main goal was to prove that even though our method (plugin) does not create a perfect language, it can be customized very fast into a very usable form.
We manually tweaked/customized the editor and the TextGen aspect only, structure aspect was left in its original form.
This justifies some of the decisions we have described in Section X (editor aspect) and Section Y (textgen), proving that our approach is quite practical (and the best\PV{?}).

@@

\PV{Veta se opakuje nize, odstranil bych tuhle}
To summarize, import languages such as JavaScript or JSON and others are giving nice results.

@@

\PV{Tohle uz neni pravda, error reporting i cyklicka pravidla jsem pred odevzdanim DP vyladil a kod celkove dodelal. Cyklicka pravidla to tedy neumi, jen na ne upozorni (a rekne, ktere pravidlo je obsahuje).}
Limitation: the project is lacking proper error reporting and cannot handle cyclic rules (which could be found in Python grammar, for example).
